SPARQL on the Open, Decentralised Web

### 2016-07-24 dissertation/problems.tex
ref new query eval prelim

It was found in \cite{perez2009semantics} that

\begin{problem}\label{prob:sparqlcomplex}
SPARQL has some highly complex parts.
\end{problem}

In particular, nested \sparql{OPTIONAL}s will be difficult to
evaluate. A Cartesian join is also likely to cause trouble, but even
seemingly straightforward queries may be heavy. We also note from
experience that:

>>>>

As discussed in \ref{sec:prelimquery},

\begin{problem}\label{prob:sparqlcomplex}
Some features of SPARQL may cause excessive endpoint load.
\end{problem}

We also note from experience that:
